Verifying Demonstrations

### 2020-04-29 paper/protocol-trusted.tex
Fixes typo in trusted (\psh_W -> \psh)

\paragraph*{Submission:
  \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t, l]\)}

@@

For individual and universal verifiability, the proof should be published on 
some permanent storage, such as the ledger~\(\TS\) by running 
\(\TSsubmit[\psh_W]\) (\cref{ledger}).

Note that it does not matter if it is the witness or the protester who makes 
\(\psh_W\) available to the verifier.
The witness could compute \(\psh_W\) during the protest and give to the 
protester immediately, but we separate these steps to show that the witness can 
postpone those extra computations while potentially running on battery.

@@

Assume that the verifier wants to verify the count for a protest~\(\prtst\).
The first thing the verifier will do, is to download all the proof 
shares~\(\psh\) from the ledger~\(\TS\), such that \(\psh \sqsubseteq \sprtst\) 
is a valid proof share for some subprotest~\(\sprtst\in\prtst\) of the 
protest~\(\prtst\).
Next, the verifier selects only those proof shares~\(\psh = (\cid, \pid, \wid, 
t, l, \corr_{\wid})\) such that \(\corr_\wid\) proves knowledge of a signature 
by \(\sskw\), where \(\CA'\) is someone the verifier trusts\footnote{%
  We note that there can be more than one \ac{CA} which the verifier trusts 
  will issue credential only to trustworthy witnesses,
  but we keep to one for the simplicity of our exposition.
}.
We denote this set of proof shares by \(\pshs\).

Next, the verifier partitions the set of proof shares~\(\pshs\) using the 
relation~\(=_\pid\) such that \(
  (\cid, \pid, \wid, t, l) =_\pid (\cid', \pid', \wid', t', l')
\) is true if \(\pid = \pid'\).
Each equivalence class \(\prf_{i, \prtst} \in \pshs/=_\pid\) is a proof of 
participation for participant \(i\).
In terms of \cref{DefParticipationCount}, the set of 
proofs~\(\prfs_\prtst^{\str, \theta} = \pshs/=_\pid\), where \(\theta = 1\) and 
\(\str(\cdot) = 1\).
Consequently, the total participation count is \(|\pshs/=_\pid|\).

>>>>

\paragraph*{Submission:
  \(\psh\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t, l]\)}

@@

For individual and universal verifiability, the proof should be published on 
some permanent storage, such as the ledger~\(\TS\) by running 
\(\TSsubmit[\psh]\) (\cref{ledger}).

Note that it does not matter if it is the witness or the protester who makes 
\(\psh\) available to the verifier.
The witness could compute \(\psh\) during the protest and give to the 
protester immediately, but we separate these steps to show that the witness can 
postpone those extra computations while potentially running on battery.

@@

Assume that the verifier wants to verify the count for a protest~\(\prtst\).
The first thing the verifier will do, is to download all the proof 
shares~\(\psh\) from the ledger~\(\TS\), such that \(\psh \sqsubseteq \sprtst\) 
is a valid proof share for some subprotest~\(\sprtst\in\prtst\) of the 
protest~\(\prtst\).
Next, the verifier selects only those proof shares~\(\psh = (\cid, \pid, \wid, 
t, l, \corr_{\wid})\) such that \(\corr_\wid\) proves knowledge of a signature 
by \(\sskw\).
We denote this set of proof shares by \(\pshs\).

Next, the verifier partitions the set of proof shares~\(\pshs\) using the 
relation~\(=_\pid\) such that \(
  (\cid, \pid, \wid, t, l) =_\pid (\cid', \pid', \wid', t', l')
\) is true if \(\pid = \pid'\).
Each equivalence class \(\prf_{i, \prtst} \in \pshs/{=_\pid}\) is a proof of 
participation for participant \(i\).
In terms of \cref{DefParticipationCount}, we let \(\theta = 1\) and \[
  \str(\psh) =
    \begin{cases}
      1 & \text{if the verifier trusts \(\CA'\) to issue only to trustworthy 
        witnesses} \\
      0 & \text{otherwise}
    \end{cases}.
\] Consequently, the total participation count is \(|\prfs_\prtst^{\str, 
\theta}|\).
